\renewcommand{\refname}{KAYNAKLAR}
 
\begin{thebibliography}{99}

\bibitem{k1} Mozilla Developer Network. (2024). \textit{HTML: HyperText Markup Language}. \url{https://developer.mozilla.org/en-US/docs/Web/HTML} [Ziyaret tarihi:\today]

\bibitem{k2} Mozilla Developer Network. (2024). \textit{CSS: Cascading Style Sheets}. \url{https://developer.mozilla.org/en-US/docs/Web/CSS} [Ziyaret tarihi:\today]

\bibitem{k3} Mozilla Developer Network. (2024). \textit{JavaScript}. \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript} [Ziyaret tarihi:\today]

\bibitem{k4} OpenJS Foundation. (2024). \textit{Node.js and Express.js}. \url{https://nodejs.org/}, \url{https://expressjs.com/} [Ziyaret tarihi:\today]

\bibitem{k5} Oracle Corporation. (2024). \textit{MySQL Database}. \url{https://www.mysql.com/} [Ziyaret tarihi:\today]

\bibitem{k6} Leaflet. (2024). \textit{Leaflet - an open-source JavaScript library for mobile-friendly interactive maps}. \url{https://leafletjs.com/} [Ziyaret tarihi:\today]

\bibitem{k7} OpenRouteService. (2024). \textit{OpenRouteService - Directions API}. \url{https://openrouteservice.org/} [Ziyaret tarihi:\today]

\bibitem{k8} OpenStreetMap Foundation. (2024). \textit{Nominatim - OpenStreetMap Geocoding}. \url{https://nominatim.openstreetmap.org/} [Ziyaret tarihi:\today]

\bibitem{k9} Auth0. (2024). \textit{JSON Web Tokens - jwt.io}. \url{https://jwt.io/}, npm. \textit{bcrypt}. \url{https://www.npmjs.com/package/bcrypt} [Ziyaret tarihi:\today]

\end{thebibliography}
